LAGOS lake depth

### 2020-03-25 figures/02_depth_model.Rmd
align axes among plots

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=3, fig.width=4.5}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ "-",
    TRUE ~ rmse)) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

ggplot(data = dt_metrics, 
                    aes(x = reorder(slope, desc(slope)), y = distance, 
                        fill = rsq)) +
  geom_tile(color = "black") +
  scale_fill_viridis_c(begin = 0.4, end = 0.7, na.value = "transparent") +
  scale_x_discrete(limits = rev(levels(dt_metrics$slope)), 
                   position = "top") +
  geom_text(aes(label = rmse), vjust = .5, fontface  = "bold", alpha = 1) +
  xlab("slope") +
  cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
```

@@

gg_shape <- lapply(unique(dt$maxdepth), function(x){ 
  ggplot(data = dplyr::filter(dt, maxdepth == x)) + 
  geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
        strip.background = element_blank(), 
        strip.text = element_blank(),
        plot.margin = unit(c(1.2,0.2,0.2,0.2), "cm"))  +
  guides(fill = guide_legend(nrow = 2))
  })
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
                                        theme(legend.direction = "horizontal") +
                                        guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none", 
                                        axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme(axis.text = element_blank(), 
                                       axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(), 
                                       axis.title = element_blank())

gg_shape <- cowplot::plot_grid(gg_shape[[1]], 
          cowplot::plot_grid(
            cowplot::plot_grid(gg_shape[[1]], gg_shape[[2]], 
                               rel_widths = c(1, 0.85)),
            cowplot::plot_grid(gg_shape[[3]], gg_shape[[4]], 
                               rel_widths = c(1, 0.85)), 
            leg, 
            nrow = 3, rel_heights = c(0.85, 1, 0.15)), 
          ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) +
  draw_label("Residual distribution", 
             x = 0.55, y = 0.99, size = 10, fontface = "bold")

@@

gg_reservoir <- cowplot::plot_grid(gg_reservoir[[1]], 
          cowplot::plot_grid(
            cowplot::plot_grid(gg_reservoir[[1]], gg_reservoir[[2]], 
                               rel_widths = c(1, 0.85)),
            cowplot::plot_grid(gg_reservoir[[3]], gg_reservoir[[4]], 
                               rel_widths = c(1, 0.85)), 
            leg, 
            nrow = 3, rel_heights = c(0.85, 1, 0.15)), 
          ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) +
  draw_label("Residual distribution", 
             x = 0.55, y = 0.99, size = 10, fontface = "bold")

cowplot::plot_grid(gg_shape, gg_reservoir, ncol = 2)
```

>>>>

```{r depth_model_metrics, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.height=2.8, fig.width=4.2}
dt_metrics <- readRDS("../data/01_depth_model/depth_grid_metrics.rds") %>%
  mutate_if(is.numeric, function(x) as.character(round(x, 2))) %>%
  mutate(rsq = as.numeric(rsq)) %>%
  mutate(rsq = case_when(
    as.character(model) == "maxdepth_true_true" ~ NA_real_,
    TRUE ~ rsq)) %>%
  mutate(rmse = case_when(
    as.character(model) == "maxdepth_true_true" ~ "-",
    TRUE ~ rmse)) %>%
  mutate(model = gsub("maxdepth_", "", model)) %>%
  mutate(model = gsub("false", "proxy", model)) %>%
  tidyr::separate(model, c("slope", "distance")) %>%
  dplyr::select(slope, distance, everything(), -.estimator)

ggplot(data = dt_metrics, 
                    aes(y = slope, 
                        x = reorder(distance, desc(distance)),
                        fill = rsq)) +
  geom_tile(color = "black") +
  scale_fill_viridis_c(begin = 0.4, end = 0.7, na.value = "transparent") +
  scale_x_discrete(limits = rev(levels(dt_metrics$slope)), 
                   position = "top") +
  geom_text(aes(label = rmse), vjust = .5, fontface  = "bold", alpha = 1) +
  xlab("distance") + ylab("slope") +
  cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
```

@@

gg_shape <- lapply(unique(dt$maxdepth), function(x){ 
  ggplot(data = dplyr::filter(dt, maxdepth == x)) + 
  geom_density(aes(x = resid, fill = shape_class), alpha = 0.75, adjust = 1.3) +
  scale_fill_manual(values = hue_pal()(3)[1:2]) +
  geom_vline(aes(xintercept = 0), linetype = "dashed") +
    xlim(-25, 25) +
    xlab("Residual") +
    theme_cowplot() +
    theme(legend.position = "bottom",
        strip.background = element_blank(), 
        strip.text = element_blank(),
        plot.margin = unit(c(1.2,0.2,0.2,0.2), "cm"))  +
  guides(fill = guide_legend(nrow = 2))
  })
gg_shape[[1]] <- ggplot() + geom_blank() + cowplot::theme_cowplot() +
  theme(axis.line = element_blank())
leg            <- cowplot::get_legend(gg_shape[[2]] + labs(fill = "Shape class") +
                                        theme(legend.direction = "horizontal") +
                                        guides(fill = guide_legend(ncol = 2)))
theme_opts     <- function(x) x + theme(legend.position = "none", 
                                        axis.title = element_blank())
rm_legend     <- function(x) x + theme(legend.position = "none")
gg_shape      <- lapply(gg_shape, rm_legend)
gg_shape[[2]] <- gg_shape[[2]] + theme(axis.text = element_blank(), 
                                       axis.title = element_blank())
gg_shape[[3]] <- gg_shape[[3]] + theme(axis.title = element_blank())
gg_shape[[4]] <- gg_shape[[4]] + theme(axis.text.y = element_blank(), 
                                       axis.title = element_blank())

gg_shape <- cowplot::plot_grid(gg_shape[[1]], 
          cowplot::plot_grid(
            cowplot::plot_grid(gg_shape[[1]], gg_shape[[2]], 
                               rel_widths = c(1, 0.85)),
            cowplot::plot_grid(gg_shape[[3]], gg_shape[[4]], 
                               rel_widths = c(1, 0.85)), 
            leg, 
            nrow = 3, rel_heights = c(0.85, 1, 0.15)), 
          ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10)#  +
  # draw_label("Residual distribution", 
  #            x = 0.55, y = 0.99, size = 10, fontface = "bold")

@@

gg_reservoir <- cowplot::plot_grid(gg_reservoir[[1]], 
          cowplot::plot_grid(
            cowplot::plot_grid(gg_reservoir[[1]], gg_reservoir[[2]], 
                               rel_widths = c(1, 0.85)),
            cowplot::plot_grid(gg_reservoir[[3]], gg_reservoir[[4]], 
                               rel_widths = c(1, 0.85)), 
            leg, 
            nrow = 3, rel_heights = c(0.85, 1, 0.15)), 
          ncol = 2, rel_widths = c(0.1, 1)) %>%
  ggdraw() +
  # draw_label("proxy", x = 0.06, y = 0.32, angle = 90, size = 10) +
  # draw_label("true", x = 0.06, y = 0.75, angle = 90, size = 10) +
  # draw_label("slope", x = 0.01, y = 0.55, size = 10, angle = 90) +
  draw_label("proxy", x = 0.8, y = 0.9, size = 10) +
  draw_label("true", x = 0.35, y = 0.9, size = 10) +
  draw_label("distance", x = 0.55, y = 0.96, size = 10) # +
  # draw_label("Residual distribution", 
  #            x = 0.55, y = 0.99, size = 10, fontface = "bold")

cowplot::plot_grid(gg_shape, gg_reservoir, ncol = 2, rel_widths = c(1, 0.9))
```
